Deep Learning Project

### 2024-10-10 project/paper.tex
Add Motivation and Inspiration sections to the paper
Updated the paper to include sections on Motivation and Inspiration to give context to the project. Also corrected the date and added new references related to the Inception model implementation and image preprocessing techniques.

\title{Deep Learning Project}
\author{
    Group Members: \\
    Farooq Mahmud
}
\date{September 28, 2024}

@@

@@

\subsubsection{Inception Architecture}
The Inception architecture was introduced to address the primary challenge in convolutional neural networks- improving model accuracy while maintaining computational efficiency. Szegedy et al. proposed a novel structure called the Inception module, which incorporates parallel convolutional filters of different sizes (1x1, 3x3, and 5x5) along with max-pooling. The key advantage of this approach is that it allows the network to capture features at multiple scales simultaneously, enhancing the model's ability to learn complex spatial hierarchies within images.

>>>>

\title{Deep Learning Project}
\author{
    Group Members: \\
    Farooq Mahmud
}

\date{October 11, 2024}

@@

\textcolor{red}{
\section {Motivation}
Attempting to reproduce the experiment from the Szegedy paper is primarily motivated by the desire to apply TensorFlow to a practical problem, such as image classification, using a realistic dataset. Recognizing that the operational environment would be constrained (i.e., running the reproduction on a desktop PC), we also saw this as an opportunity to evaluate the network's performance on a smaller version of the ImageNet dataset. This project allowed us to directly experience the challenges of training a neural network. Additionally, it provided valuable experience in writing TensorFlow code for a complex neural network with branching and joining structures, whereas our prior work has been limited to simpler, sequential networks.}

\textcolor{red}{
\section{Inspiration}
Two code bases served as the inspiration for our Tensorflow implementation of Inception. The image pre-processing, particularly regularization techniques were guided by \cite{dishasai_multiclass_classification}. The Inception layer implementation was inspired by \cite{googlenet_inception_module}. Lastly, the graphs in Figures \ref{fig:googlenet-simple-accuracy} and \ref{fig:googlenet-complex-accuracy} were inspired by \cite{datacamp_cnn_tensorflow}.}

@@

\subsection{Inception Architecture}
The Inception architecture was introduced to address the primary challenge in convolutional neural networks- improving model accuracy while maintaining computational efficiency. Szegedy et al. proposed a novel structure called the Inception module, which incorporates parallel convolutional filters of different sizes (1x1, 3x3, and 5x5) along with max-pooling. The key advantage of this approach is that it allows the network to capture features at multiple scales simultaneously, enhancing the model's ability to learn complex spatial hierarchies within images.
